Evaluating the evidence of widespread maintenance of functional composition in vertebrate communities

### 2021-10-01 paper/manuscript.Rmd
still going

We observed no significant trends within taxa No significant differences between taxa.
Indicates that we could've looked at any taonomic subset of the data and gotten the same result.
But what does that mean for taxa we left out?
We can only make educated guesses based on what we know of the ecology of taxa that were left out - taxa specific papers?

What does local maintenance of functional structure mean for the function of these communities?
The vast majority of experimental and observational work links function to changes in functional or species diversity.
By those criteria, very few observed communities in our dataset are in a state of concern for declining functionality.
However, we did not we did not directly measure some aspects of community structure important for ecosystem multifunctionality [e.g. dispersion, rarity, abundance of dominant species; @bagousse-pinguet2021].
While our metrics indirectly incorporate dimensions of the functional space related to those characteristics, they are likely not sensitive enough to infer deterioration (or improvement) in those those aspects of structure.
<!-- more citations please -->

@@

While we did not directly measure changes in rare species, our results also contradict likely scenarios of loss predicted due to rare species extinction.
Rare species, defined by small populations and geographic restriction, are simultaneously more likely to be functionally distinct and at higher risk for extinction [@davies2004; @harnik2012; @loiseau2020]. Assuming local extirpation is a precursor to global extinction, communities losing functionally rare species should exhibit strong functional shifts as lost species cannot be replaced by functionally similar species [@leitão2016] .
Instead, these communities appear to only have turnover of species with functionally redundant species in the species pool.

>>>>

We observed no significant trends within taxa No significant differences between taxa.
Indicates that we could've looked at any taxonomic subset of the data and gotten the same result.
But what does that mean for taxa we left out?
We can only make educated guesses based on what we know of the ecology of taxa that were left out - taxa specific papers?

What does local maintenance of functional structure mean for the function of these communities?
The vast majority of experimental and observational work links declines in function to declines in functional or species diversity [@brose2016; @cadotte2011; @duffy2007] . By those criteria, very few observed communities in our dataset are in a state of concern for loss of functionality. However, we did not we did not directly measure some aspects of community structure important for ecosystem multifunctionality [e.g. dispersion, rarity, abundance of dominant species; @bagousse-pinguet2021].
While our metrics indirectly incorporate dimensions of the functional space related to those community characteristics, they are likely not sensitive enough to infer deterioration (or improvement).
<!-- more citations please -->

-   experiments vs broad scale observational studies - do we look at FD in both?

@@

While we did not directly measure changes in rare species, our results also contradict likely scenarios of loss predicted due to rare species extinction.
Rare species, defined by small populations and geographic restriction, are simultaneously more likely to be functionally distinct and at higher risk for extinction [@davies2004; @harnik2012; @loiseau2020]. Locally, communities losing functionally rare species should exhibit strong functional shifts as lost species cannot be replaced by functionally similar species [@leitão2016] .
Instead, we observed patterns consistent with species replacement by functionally redundant species from the species pool.
